---
title: "Coursera Plotly Assignment"
author: "JB"
date: "January 8, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Medical Image Viewing in Plotly

Plotly has a lot of great built-in features for looking at greyscale images,
including medical images in non-DICOM formats.  These features include zooming,
panning, region of interest selection and image intensity displays at specific
pixel locations.  This code reads in a greyscale jpg image of a slice of a cone-beam
computed tomography (cone beam CT) scan of someone's head.  The image was rotated
and converted into an 8-bit image (256 greyscale intensity values from 0-255).  Regions
of the image that have intensity 0 are completely dark, while regions at 255 intensity
level (such as the skull bone), look white.  Everything in between is a different shade
of gray.  It is also often useful to have a histogram of grayscale intensities from 
the image as well, to show how many pixels in the image have each grayscale value.
```{r image, message=FALSE, warning=FALSE}
library(plotly)
library(imager)
set.seed(5150)
image_data <- load.image("ConeBeam_CT_Head.jpg")
dimensions <- dim(image_data)

image_data <- as.matrix(image_data[,,1,1], nrow=444, ncol=355)
image_data <-t(image_data)
image_data <- apply(image_data,2,rev)
image_data <- image_data*255
image_display <-plot_ly(z=~image_data, type = "heatmap", colors  = 'Greys', 
    reversescale = T)
image_display
```


Code to produce a histogram of greyscale image intensities in Plotly.  There are a 
large number of pixels with an intensity of either 0 or 255, and a mound-like 
distribution of pixel intensities around the 100 level value.
```{r image_histogram, warning=FALSE}
hist_data <- as.vector(image_data)
hist_display <- plot_ly(x=~hist_data, type = "histogram",
    marker = list(color='limegreen')) %>% 
layout(title= "Pixel Histogram", xaxis=list(title="Pixel Intensity"),
    yaxis=list(title="Counts"))
hist_display
```